---
title: "Matthew Bain's resume"
author: Matthew Bain
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css:
      - !expr fs::path_package("autocv", "extdata", "css/custom_resume.css")
      - !expr fs::path_package("autocv", "extdata", "css/styles_html.css")
      - "resume"
    self_contained: true
params:
  # "PDF" or "HTML" is automatically updated in render_resume.R
  doctype: "PDF"
  resume_data_filename: "resume_data.xlsx"
  target: "base"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(autocv)
library(glue)
library(dplyr)

# Source helpers for dev
# source('R/preprocess.R')
# source('R/print_cv.R')

# fs::dir_ls(get_path_to("extdata"))

target <- "base"

# Load data and preprocess
position_data <- autocv::load_application_data(
  target = target,
  filename = "resume_data.xlsx",
  sheet = "entries",
  skip = 1
) %>% 
  autocv::preprocess_entries(
    ., 
    style = "markdown", 
    order = "reversed", 
    bullet_style = "-"
  )

skill_data <- autocv::load_application_data(
  target = target,
  filename = "resume_data.xlsx",
  sheet = "skills",
  skip = 2
)

contact_data <- autocv::load_application_data(
  target = target,
  filename = "cover_data.xlsx",
  sheet = "contact_info"
) %>% autocv::preprocess_contacts(., style = "markdown")

text_data <- autocv::load_application_data(
  target = target,
  filename = "cover_data.xlsx",
  sheet = "text_blocks"
) %>% autocv::preprocess_text()

```

```{r extract, include=FALSE}

name <- contact_data$address_text[contact_data$loc == "name"]
role <- text_data$text[text_data$loc == "title"]
bio <- text_data$text[text_data$loc == "bio"]
suffix <- contact_data$address_text[contact_data$loc == "title"]

pic_text <- glue::glue_collapse(
  contact_data[contact_data$loc == "pic",]$contact_text
)
contact_text <- autocv::print_contact_info(
  contact_data, 
  section = "both", 
  sep = "\n"
)

```

# Aside

`r paste(pic_text)`

## Contact {#contact}

`r paste(contact_text)`

```{r download}

# If `doctype` is html add link to download a pdf version
if(params$doctype == "HTML"){
  paste0(
    "[<i class='fas fa-download'></i> Download as a PDF]",
    "(https://github.com/bainmatt/resume/main/bainmatt_resume.pdf)"
  ) %>% 
  glue::glue_collapse(sep = "\n")
}

```

## Core tools {#tech}

```{r tech, dev.args = list(bg = 'transparent')}

autocv::build_skill_bars(skill_data %>% dplyr::filter(core_tools == "x"))

```

## Current tech {#stack}

```{r stack, dev.args = list(bg = 'transparent')}

autocv::build_skill_bars(skill_data %>% dplyr::filter(current_tech == "x"))

```

## Key competencies {#skills}

```{r skills, dev.args = list(bg = 'transparent')}

autocv::build_skill_bars(skill_data %>% dplyr::filter(key_competency == "x"))

```

<!-- ## Disclaimer {#disclaimer} -->

<!-- ```{r} -->

<!-- # Set disclaimer in bottom right corner based on `doctype` -->
<!-- if(params$doctype == "HTML") { -->
<!--   glue::glue(" -->
<!--     Made w/ [**pagedown**](https://github.com/rstudio/pagedown). -->
<!--     Source code: [**Github repo**](https://github.com/mleary/resume). -->
<!--   ") -->
<!-- } -->
<!-- if(params$doctype == "PDF") { -->
<!--   glue::glue(" -->
<!--     Made w/ **pagedown::html_resume** -->
<!--     Code: **github.com/mleary/resume** -->
<!--   ") -->
<!-- } -->
<!-- ``` -->

Last updated on `r Sys.Date()`. <br> <br>

# Main

## `r paste0(name, ", ", suffix)` {#title}

### `r paste(role)`

`r paste(bio)`

## Professional Experience {data-icon="suitcase"}

```{r jobs}
autocv::print_section(position_data, 'work')
```

## Education {data-icon="graduation-cap" data-concise="true"}

```{r education}
autocv::print_section(position_data, 'education')
```

## Certifications {data-icon="award" data-concise="true"}

```{r certificates}
autocv::print_section(position_data, 'certifications')
```

## Selected Projects {data-icon="code-branch" data-concise="true"}

```{r projects}
autocv::print_section(position_data, 'projects')
```

## Selected Writing {data-icon="laptop" data-concise="true"}

```{r writing}
autocv::print_section(position_data, 'writing')
```

## Selected Publications {data-icon="file" data-concise="true"}

```{r articles}
autocv::print_section(position_data, 'publications')
```

## Additional information {data-icon="circle-user" data-concise="true"}

```{r other}
autocv::print_section(position_data, 'additional_information')
```
