---
title: "Demo of autocv"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demo of autocv}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(autocv)
```

In this demo I cover the fundamental end-to-end workflow involved in creating
and managing tailored job applications using `autocv`.

## A minimal reproducible example

The following end-to-end example runs in a temporary environment on your
local machine, constructing a project directory, an application directory,
a resume, and keyword reports, all from the `autocv`-supplied
example job posting, template datasets, and template stylesheets.

```{r reproducible-demo, eval=FALSE}
autocv::in_tmp_env({
  message("1. Build the project directory...")
  autocv::build_base_directory()

  data(example_job_metadata)
  app_df <- autocv::construct_app_metadata(app_info = example_job_metadata)

  message("")
  message("2. Build the application...")
  autocv::build_app_directory(app_df = app_df, open = FALSE)

  message("")
  message("3. Render the application...")
  # autocv::render_app(cover = FALSE, email = FALSE)
  autocv::render_resume_plain()

  message("")
  message("4. Check application keywords...")
  report_df <- autocv::check_skills()
  print(report_df)

  message("")
  message("5. Inspect application metadata...")
  app_df <- autocv::get_app_info()
  print(app_df)
})
```

## A step-by-step example

Let us now walk through each of these steps in greater depth,
keeping track of the evolving file tree
and copying the generated documents from the temporary environment
to your working directory for reference later.

### Step 1: Build the project directory

We begin by creating the basic file tree
upon which to build tailored job applications. The file tree includes
placeholder `output/` and `applications/` directories that store generated
documents, as well as an `input/` directory containing the template
spreadsheets
[`resume_data.xlsx`](https://github.com/bainmatt/autocv/blob/main/inst/templates/template_resume_data.xlsx)
(see [`example_skill_data`](../reference/example_skill_data.html) and
[`example_position_data`](../reference/example_position_data.html)),
[`cover_data.xlsx`](https://github.com/bainmatt/autocv/blob/main/inst/templates/template_cover_data.xlsx)
(see [`example_contact_data`](../reference/example_contact_data.html) and
[`example_text_data`](../reference/example_text_data.html)), and
`job_metadata.yml`
([`example_job_metadata`](../reference/example_job_metadata.html)).
A `.Rprofile` file
containing path environment variables is automatically generated,
along with an `Rproj` file and the notebooks
[`resume.Rmd`](https://github.com/bainmatt/autocv/blob/main/inst/templates/template_resume.Rmd) and
[`cover.Rmd`](https://github.com/bainmatt/autocv/blob/main/inst/templates/template_cv.Rmd),
which are used to render job application documents
from data contained in the aforementioned spreadsheets.

```{r build-base}
autocv::in_tmp_env({
  autocv::build_base_directory()
})

```

```{r, echo=FALSE}
autocv::in_tmp_env({
  message("Current file tree:")
  fs::dir_tree(autocv::get_path_to("notebooks"))
})

```

### Step 2: Build the application directory

With the project directory constructed and template data files copied over,
we can now generate tailored job applications. To do so, you should
update the fields in the `input/job_metadata.yml` file with information
relevant to the job of interest, namely the `id`, `company`, `position`,
and `posting_url` fields, as well as optionally populating the
`base_id`, `portal_url`, `linkedin_url`, `recruiter_email`, and `notes`
fields. For additional information, see
[`example_job_metadata`](../reference/example_job_metadata.html).


```{r build-app}
autocv::in_tmp_env({
  data(example_job_metadata)
  app_df <- autocv::construct_app_metadata(app_info = example_job_metadata)
  autocv::build_app_directory(app_df = app_df, open = FALSE)
})

```

```{r, echo=FALSE}
autocv::in_tmp_env({
  message("Current file tree:")
  fs::dir_tree(autocv::get_path_to("applications"))
})

```

### Step 3: Edit the application

After building the application directory, run `autocv::edit_app()`. This will
open the spreadsheets, namely
[`resume_data.xlsx`](https://github.com/bainmatt/autocv/blob/main/inst/templates/template_resume_data.xlsx) and
[`cover_data.xlsx`](https://github.com/bainmatt/autocv/blob/main/inst/templates/template_cover_data.xlsx),
containing the data that will be used to generate your
application documents. Edit the entries and metadata in these documents
as desired to suit the job in question.

### Step 4: Render the application

Once you've tailored the information in your application
to the job in question, you are ready to render your application documents.

```{r render-app}
autocv::in_tmp_env({
  # autocv::render_app(cover = FALSE, email = FALSE)
  autocv::render_resume_plain()
})

```

```{r, echo=FALSE}
autocv::in_tmp_env({
  message("Current file tree:")
  fs::dir_tree(autocv::get_path_to("applications"))
})

```

### Step 5: Check application keywords

Having generated a resume, we can now analyze its contents
to determine which data-related keywords we included and whether
they align with the keywords in the job posting. This step
performs three independent checks -- identify general job-related
keywords in the job posting, identify data science keywords
in the job posting, identify data science keywords in the resume --
followed by a keyword match of the data science terms from the job posting
against those mentioned in the resume, either in the skills section or in the
body text.

```{r check}
autocv::in_tmp_env({
  report_df <- autocv::check_skills()
  print(report_df)
})

```

```{r, echo=FALSE}
autocv::in_tmp_env({
  message("Current file tree:")
  fs::dir_tree(autocv::get_path_to("applications"))
})

```

The following spreadsheets were generated by this step:

- [`keyword_counts_AB.csv`](https://github.com/bainmatt/autocv/blob/main/vignettes/output/keyword_counts_AB.csv): General keyword counts for the job posting
- [`skill_counts_posting_AB.csv`](https://github.com/bainmatt/autocv/blob/main/vignettes/output/skill_counts_posting_AB.csv): Data-related keyword counts for the job posting
- [`skill_counts_resume_AB.csv`](https://github.com/bainmatt/autocv/blob/main/vignettes/output/skill_counts_resume_AB.csv): Data-related keyword counts for the generated resume
- [`skill_report_AB.csv`](https://github.com/bainmatt/autocv/blob/main/vignettes/output/skill_report_AB.csv): Job posting keywords included in the generated resume

### Step 6: Inspect application metadata

Every step so far has yielded metadata that was automatically stored in
a log file, with each row corresponding to a unique job application.
If at any point you wish to review the information for an existing
job application, you can easily retrieve it from the log.

```{r inspect}
autocv::in_tmp_env({
  app_df <- autocv::get_app_info()
  print(app_df)
})

```

### Step 7: Update application metadata

At this point we can update the job application log with new information
as desired, such as changes to the status of the application or a note
about the job in question.

```{r update}
autocv::in_tmp_env({
  autocv::apply_to(app_id = "AB")
  autocv::update_app_info(app_id = "AB", notes = "Excited about this role")

  app_df <- autocv::get_app_info()
  print(app_df)
})

```

## Review the generated documents

Let's conclude by transferring some of documents generated within our
temporary environment into long-term memory. Each `autocv`-generated
application document is displayed below for reference.

```{r log-files}
autocv::in_tmp_env({
  source_paths <- as.character(autocv::get_app_info(
    id = "AB",
    field = c(
      "resume_plain_path",
      "keyword_counts_posting",
      "skill_counts_posting",
      "skill_counts_resume",
      "skill_report"
    )
  )[2:6])
  target_dir <- file.path(fs::path_wd(), "output")
  if (!dir.exists(target_dir)) { dir.create(target_dir) }
  target_paths <- file.path(target_dir, basename(source_paths))

  autocv::copy_files(
    source_paths = source_paths,
    target_paths = target_paths
  )
})

```

```{r, echo=FALSE}
autocv::in_tmp_env({
  message("Working directory output file tree:")
  fs::dir_tree(file.path(fs::path_wd(), "output"))
})

```

```{r, include=FALSE}
evaluate_chunks <- FALSE
knitr::opts_chunk$set(eval = evaluate_chunks)

```

```{r render-cv}
# NOTE: eval is off due to LaTeX rendering issues when running GitHub workflow
autocv::in_tmp_env({
  autocv::render_cv_as_html()
  autocv::render_resume()
})

```

```{r log-base-files}
autocv::in_tmp_env({
  source_paths <- c(
    as.character(autocv::get_app_info(id = "AB", field = "resume_path")[2]),
    file.path(autocv::get_path_to("output"), "cv_yourname.html")
  )
  target_dir <- file.path(fs::path_wd(), "output")
  if (!dir.exists(target_dir)) { dir.create(target_dir) }
  target_paths <- file.path(target_dir, basename(source_paths))

  autocv::copy_files(
    source_paths = source_paths,
    target_paths = target_paths
  )
})

```

```{r build-html, eval=TRUE}
filename <- "cv_yourname.html"
source_path <- file.path(
  autocv::get_path_to("notebooks"), "vignettes", "output", filename
)
target_path <- file.path(
  autocv::get_path_to("notebooks"), "docs", filename
)
file.copy(source_path, target_path, overwrite = TRUE)

```

The following documents were generated by `autocv`:

- [`resume_yourname_AB.pdf`](https://github.com/bainmatt/autocv/blob/main/vignettes/output/resume_yourname_AB.pdf) (PDF resume):

<br>
<object data="output/resume_yourname_AB.pdf" type="application/pdf" width="100%" height="500px" style="padding:10px">
  <p>Unable to display PDF file. <a href="output/resume_yourname_AB.pdf">Download</a> instead.</p>
</object>
<br>

- [`cv_yourname.html`](https://bainmatt.github.io/autocv/cv_yourname.html) (web-based CV):

<br>
<object data="output/cv_yourname.html" type="text/html" width="100%" height="500px" style="padding:10px">
  <p>Unable to display HTML file. <a href="output/cv_yourname.html">Download</a> instead.</p>
</object>
<br>

- [`resume_yourname_AB.txt`](https://github.com/bainmatt/autocv/blob/main/vignettes/output/resume_yourname_AB.txt) (plain text resume):

<br>
<object data="output/resume_yourname_AB.txt" type="text/plain" width="100%" height="500px" style="padding:10px">
  <p>Unable to display text file. <a href="output/resume_yourname_AB.txt">Download</a> instead.</p>
</object>
<br>

<!-- <br> -->
<!-- <object data="templates/template_resume_data.xlsx" type="application/vnd.openxmlformats-officedocument.spreadsheetml.sheet" width="100%" height="500px" style="padding:10px"> -->
<!--   <p>Unable to display spreadsheet. <a href="templates/template_resume_data.xlsx">Download</a> instead.</p> -->
<!-- </object> -->
<!-- <br> -->

And there you have it! A few steps
("build, edit, render, check" and "inspect, update"), neatly encapsulated
within `autocv`'s core user interface, are all you need to construct
beautiful, tailored, easily tracked, resume documents and job applications.
