---
title: "Build a CV using autocv"
subtitle: |
    I walk through the basic steps involved in generating a CV using `autocv`.
toc: true
toc-depth: 2

output: rmarkdown::html_vignette
vignette: >
 %\VignetteIndexEntry{Build a CV using autocv}
 %\VignetteEngine{knitr::rmarkdown}
 %\VignetteEncoding{UTF-8}
params:
  doctype: "HTML"
---

In this vignette I will cover the fundamental use case for this package: 
automatically building a resume from spreadsheet data. If you have no interest
in customizing or building upon the tools in this package, then you can
safely ignore the [Reference](../reference/index.html) 
section of this documentation and just follow along with this article.

---

WIP. This article was written for a now-outdated version of autocv, and
as a result may contain outdated information.
Stay tuned for revisions, and in the meantime refer to the
[User Interface roadmap](../index.html#user-interface) and the
[API Reference](../reference/index.html) for usage guidelines.
   
---

# Installation

{
How to install from tar (put this in Readme)
}

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = TRUE
)
```

# Data prep

Let's walk through the process with an end-to-end example using some
fake data. The first step is to load the data, which we can do with
the `data()` function since the datasets we will be using are included
in `autocv`.

----

```{r load, include=TRUE}
# Load packages
library(autocv)

library(glue)
library(readxl)
library(stringr)
library(magrittr, warn.conflicts = FALSE)
library(dplyr, warn.conflicts = FALSE)

# Load data and preprocess
data("example_position_data", package = "autocv")
position_data <- example_position_data %>%
  autocv::preprocess_entries(
    style = "markdown", 
    order = "reversed", 
    bullet_style = "-"
  )

data("example_skill_data", package = "autocv")
skill_data <- example_skill_data

data("example_contact_data", package = "autocv")
contact_data <- example_contact_data %>% 
  autocv::preprocess_contacts(., style = "markdown")

data("example_text_data", package = "autocv")
text_data <- example_text_data %>% 
  autocv::preprocess_text()

```

----

Let's now do some pre-processing to get these sections into a format that
can be displayed in R Markdown:

----

```{r extract}

name <- contact_data$address_text[contact_data$loc == "name"]
role <- text_data$text[text_data$loc == "title"]
bio <- text_data$text[text_data$loc == "bio"]
suffix <- contact_data$address_text[contact_data$loc == "title"]

pic_text <- glue::glue_collapse(
  contact_data[contact_data$loc == "pic",]$contact_text
)
contact_text <- autocv::print_contact_info(
  contact_data, 
  section = "both", 
  sep = "\n"
)

```

----

# Margin

The first element of the CV is the `aside`, which contains the contact
information and any skills you choose to include in the 
right margin of the CV.

We print the following header to tell `pagedown` when this section starts: 

----

```{r aside-header, eval=FALSE}
glue("# Aside")
```

----

<!-- `r paste(pic_text)` -->

## Contact information {#contact}

The contact card ... 

We need the following header:

----

```{r contact-header, eval=FALSE}
glue("## Contact {{#contact}}")
```

----

We then print the contact card as follows:

----

```{r links}
contact_text
```

<!-- `r paste(contact_text)` -->

----

## Download link

You may wish to include a link to download ...

----

```{r download}

# If `doctype` is html add link to download a pdf version
if(params$doctype == "HTML"){
  paste0(
    "[<i class='fas fa-download'></i> Download as a PDF]",
    "(https://github.com/bainmatt/resume/main/bainmatt_resume.pdf)"
  ) %>% 
  glue::glue_collapse(sep = "\n")
}

```

----

## Skills

The skills ... 

You may wish to give these sections headers:

----

```{r skills-header, eval=FALSE}
glue("## Skills")
```

----

You would then print the corresponding skill bars as follows:

----

```{r tech, dev.args = list(bg = 'transparent')}
autocv::build_skill_bars(filter(skill_data, core_tools == "x"))
```

## Datestamp

You may wish to include a datestamp to ...

----

```{r datestamp}
glue("Last updated on ", "{Sys.Date()}")
```

<!-- Last updated on `r Sys.Date()`. -->

----

# Main section

We print the following header to tell `pagedown` when this section starts: 

----

```{r main-header, eval=FALSE}
glue("# Main")
```

<!-- # Main -->

----

## Title

Your title ...

----

```{r header, eval=FALSE}
glue("## ", "{name}, ", "{suffix}", " {{#title}}")
```

<!-- ## `r paste0(name, ", ", suffix)` {#title} -->

----

## Role

Your role ...

----

```{r role, eval=FALSE}
glue("### ", "{role}")
```

<!-- ### `r paste(role)` -->

----

## Bio

Your bio is a one-paragraph-long synopsis of what you bring to the table
and what you're looking for. The `example_skill_data()` dataset includes 
two sections, each a single sentence: `experience` and `objective`:

----

```{r bio}
glue("{bio}")
```

<!-- `r paste(bio)` -->

----

# Position sections

The remaining sections, as we'll see, are all printed in the same way:

1. First we print the header with an icon from the font-awesome library.
2. Then we print the section using the `print_section()` function.

## Professional Experience

First we print the header:

----

```{r work-header, eval=FALSE}
glue("## Professional Experience ", "{{data-icon='suitcase'}}")
```

<!-- ## Professional Experience {data-icon="suitcase"} -->

----

Then we print the content:

----

```{r jobs}
autocv::print_section(position_data, "work", target = "app")
```

----

## Education

First we print the header:

----

```{r education-header, eval=FALSE}
glue("## Education ", "{{data-icon='graduation cap' data-concise='true'}}")
```

<!-- ## Education {data-icon="graduation-cap" data-concise="true"} -->

----

Then we print the content:

----

```{r education}
autocv::print_section(position_data, "education", target = "app")
```

----

## Certifications

First we print the header:

----

```{r certificates-header, eval=FALSE}
glue("## Certifications ", "{{data-icon='award' data-concise='true'}}")
```

<!-- ## Certifications {data-icon="award" data-concise="true"} -->

----

Then we print the content:

----

```{r certificates}
autocv::print_section(position_data, "certifications", target = "app")
```

----

## Selected Projects

First we print the header:

----

```{r projects-header, eval=FALSE}
glue("## Selected Projects ", "{{data-icon='code-branch' data-conside='true'}}")
```

<!-- ## Selected Projects {data-icon="code-branch" data-concise="true"} -->

----

Then we print the content:

----

```{r projects}
autocv::print_section(position_data, "projects", target = "app")
```

----

# Adding position sections

You aren't restricted to these particular sections. You may wish to change
or add to them by modifying the `loc` column in your `position_data` 
spreadsheet (see the `example_position_data()` dataset for reference). 
Some other possible sections you might wish to include are: 

- Selected Publications
- Selected Writing
- Additional Information

----

# Putting it together

To see what the finished product looks like, you can:

1. Copy/paste each code block in this article into an R chunk within 
an R Markdown notebook in your project directory
2. Add the following yaml and knitr headers to the top of the document:

```{yaml}
---
title: "My resume"
output:
  pagedown::html_resume:
    self_contained: true
params:
  doctype: "HTML"
---
```
  
```{r}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

```

3. Knit.

The resulting R Markdown notebook should look like [this](Github_link).
Knitting it will give the output [here](Github_link).

----

# Customization

The repository for this package also includes:

1. Custom css stylesheets:
   
- [`inst/css/custom_resume.css`](link)
- [`inst/css/styles_html.css`](link)
- [`inst/css/styles_pdf.css`](link)

To apply these styles, modify the output field of your yaml block as follows:

    output:
      pagedown::html_resume:
        css: ['inst/css/custom_resume.css', 'inst/css/styles_html.css', 'resume']
        self_contained: true

2. More sophisticated Excel spreadsheets housing the resume data
in multiple sheets, with guidelines and conditional formatting 
to help you adhere to them:

- [`R/data/resume_data.xlsx`](link)
- [`R/data/cover_data.xlsx`](link)

3. Convenience functions for rendering the resume:

- [`render_resume.R`](link)

4. Equivalent tools for creating resumes and cover letters with different 
formats.

----

To make the most of these tools, I recommend you clone the files into
the corresponding directories on your computer and modify the contents of
the following files using what we've covered here: 

- [`cv.Rmd`](link)
- [`R/data/resume_data.xlsx`](link)

View a complete example, with custom CSS styling applied, [here](link).

----

```{r comment='', eval=TRUE}
# cat(
#   readLines(fs::path_package("autocv", "extdata", "templates/example-cv-output.Rmd")),
#   sep = '\n'
# )
```

----

Alternatively, to create a resume or cover letter with a different format,
you can try one of the following. Each option operates on the same data files.

For a concise LaTeX resume, you will need: 

- [`inst/latex/preamble.tex`](link) (in place of any custom CSS)
- [`resume.Rmd`](link) (in place of cv.Rmd)

View an example [here](link).

For a plain text resume, you only need:

- [`plain_resume.R`](link)

View an example [here](link).

----

# Diagnositics

One last note. By building a plain text resume, providing a link to a 
job posting of interest, and running [], we get various helpful diagnostics 
for free, including a breakdown of skills, ... . For example, 
using the fake job posting [here](link) and running [] on the example data
used in this article, we obtain the following report, which opens in 
a plain text file:

> []

Just make sure to clone the following files:

- []

----

And that's the gist of it. 
Thanks to Nick Strayer for laying the groundwork for this package.

----

# Appendix: Other skills formats

To format the skills sections as a list of bold headers with a preset separator
character, we have to do a little additional preparation:

----

```{r skill-list-prep, echo=TRUE}
skill_list <- autocv::build_skill_list(
  autocv::sort_skills(skill_data), 
  sep = " • ",
  separate_competencies = TRUE,
  competencies_header = "Other"
)
```

----

The list can then be rendered as:

----

```{r skill-list, echo=TRUE}
glue("{skill_list}")
```

----
